The Jester joke recommender system

### 2020-08-02 inst/jester.Rmd
say explicitly how jester and maxjest are calculated
label entries, also some rewriting

@@

```{r }
library("hyper2",quietly=TRUE)
a <- read.csv("jester-data-3.csv",head=FALSE) # File is 150 lines only
a <- as.matrix(a[,-c(1,100)])
a[a==99] <- NA
colnames(a) <- paste("joke",sprintf("%02d",seq_len(ncol(a))),sep="")
a[1,]
```

Row 1 of `a` is displayed and shows that the first respondent rated
joke 5 at -1.65, joke 7 at -0.78, and so on; `NA` means that that
respondent did not rank that joke.  We can perform some summary
statistics of `a`:

```{r}
plot(rowSums(!is.na(a)),xlab="respondent")
```

@@

```{r}
plot(colSums(!is.na(a)),xlab="joke index")
```

@@

```{r}
dim(a)
a <- a[,colSums(!is.na(a))>1]
dim(a)
```

@@

```{r}
f <- function(x){
    x <- x[!is.na(x)]
    x[order(x,decreasing=TRUE)] <- seq_along(x)
    return(x)
}
f(a[1,])
```

@@

```{r,calculate_jester,cache=TRUE}
jester <- hyper2(pnames=colnames(a))
system.time(for(i in seq_len(nrow(a))){jester %<>% order_obs(f(a[i,]))})
```

@@

```{r,cache=TRUE}
system.time(mjest <- maxp(jester,n=1))
```

@@

```{r}
mjest
plot(mjest)
```

```{r,cache=TRUE}
equalp.test(H,startp=indep(mjest))
```

>>>>

(this file creates objects `jester` and `maxjest`, which are datasets
available in the `hyper2` package, and documented at `jester.Rd`.
This file takes quite a long time to run).

@@

```{r,label=kickoff}
library("hyper2",quietly=TRUE)
a <- read.csv("jester-data-3.csv",head=FALSE) # File is 150 lines only
a <- as.matrix(a[,-c(1,100)])
a[a==99] <- NA
colnames(a) <- paste("joke",sprintf("%02d",seq_len(ncol(a))),sep="")
a[1,]
```

Row 1 of `a` is displayed (most entries are `NA`, signifying that
respondent 1 did not rank that particular joke).  It shows that the
first respondent rated joke 5 at -1.65, joke 7 at -0.78, and so on.
We can perform some summary statistics of `a`:

```{r,label=plothowmanyjokes}
plot(rowSums(!is.na(a)),xlab="respondent")
```

@@

```{r,label=plothowmanyrespondents}
plot(colSums(!is.na(a)),xlab="joke index")
```

@@

```{r,label=removeunratedjokes}
dim(a)
a <- a[,colSums(!is.na(a))>1]
dim(a)
```

@@

```{r,label=transformthedataset}
f <- function(x){
    x <- x[!is.na(x)]
    x[order(x,decreasing=TRUE)] <- seq_along(x)
    return(x)
}
f(a[1,])
```

@@

```{r,label=calculate_jester,cache=TRUE}
jester <- hyper2(pnames=colnames(a))
system.time(for(i in seq_len(nrow(a))){jester %<>% order_obs(f(a[i,]))})
```

@@

```{r,label=findmaxp,cache=TRUE}
system.time(mjest <- maxp(jester,n=1))
```

@@

```{r,showmjest}
mjest
plot(mjest)
```

```{r,label=equalptestdoer,cache=TRUE}
equalp.test(jester,startp=indep(mjest))
```
